Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-19 programming23/paper.tex
reword 'hobbyist'

% TODO BEFORE SUBMISSION
% - units on all plots

% TODO BEFORE FINAL
% - explain edit range computations
% - uncomment acks
% - update all refs to artifacts to no longer be in future tense

@@

Due to the broad community of creators, the goals of the Luau type
system are rather unique~\cite{bfj-hatra-2021}.
Whereas a traditional type system focuses on compilation and memory
safety, Luau takes a lenient approach by default and lets creators
gradually~\cite{st-sfp-2006,tf-popl-2008} migrate to rigorous checks
one module at a time.
In this way, for example,
students in code camps may begin in the \mnocheck{} mode that reports only
syntax errors; hobbyists can use \mnonstrict{} mode to identify
would-be runtime errors; and developers who need to ensure software
quality can rely on \mstrict{} mode.
Also, no matter the mode, a {\FS{}} type analysis runs to guide \IDE{} tools~(\cref{s:context}).
Luau's types aim to support untyped designs, in the spirit of migratory
typing~\cite{tfffgksst-snapl-2017}, so that creators can switch modes without
needing to restructure their code in major, potentially-breaking, ways.

>>>>

% TODO BEFORE FINAL
% - update all refs to artifacts to no longer be in future tense

@@

Due to the broad community of creators, the goals of the Luau type
system are rather unique~\cite{bfj-hatra-2021}.
Whereas a traditional type system focuses on compilation and memory
safety, Luau takes a lenient approach by default and lets creators
gradually~\cite{st-sfp-2006,tf-popl-2008} migrate to rigorous checks
one module at a time.
The \mnocheck{} mode reports only syntax errors,
the \mnonstrict{} mode reports would-be runtime errors and skips over
other issues,
and the \mstrict{} mode reports a variety of potential errors.
In addition, no matter the mode, a {\FS{}} type analysis runs to guide \IDE{} tools~(\cref{s:context}).
Luau's types aim to support untyped designs, in the spirit of migratory
typing~\cite{tfffgksst-snapl-2017}, so that creators can switch modes without
needing to restructure their code in major, potentially-breaking, ways.
